Algorithmically Trading like a Human with GPT-J

### 2021-10-05 paper.tex
.gitignore fix

\documentclass[conference]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{svg}
\usepackage{float}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}
\usepackage{flushend}
% \usepackage{balance}
\begin{document}

@@

By our estimation, the vast majortity of previous works involving sentiment analysis used a pre-processing step to extract sentiment from the news, and then embedded those features into a time-series dataset. News sources were often limited to headlines, tweets and small snippits because of the memory limitations of RNN sentiment classifiers. With the indruduction of large transformer networks \cite{Vaswani2017}, capable of processing large amounts of text like OpenAi's GPT-3 \cite{Brown2020} or GPT-J \cite{gpt-j}, we believe a new class of trading network can be created. Our method will encode the current world state in a large text-input wich combines sentiment, real-world facts, and stock price data into a single input. We believe that this new network can be trained to learn to trade like a human.

@@

\begin{figure}[h]
    \centering
    \scalebox{0.8}{
    \definecolor{lblue}{RGB}{220, 234, 240}
    \definecolor{dblue}{RGB}{0, 21, 79}
    \newcommand\bluebox[3]{\filldraw [draw=dblue,fill=lblue, line width=0.4mm] (#1-1.75,#2-0.75) rectangle (#1+1.75,#2+0.75) node[text=dblue, font=\footnotesize][midway] {\makecell[l]{#3}}}
    \newcommand\bluearrow[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2-0.75) -- (#3,#4+0.75);}
    \newcommand\bluearrownooffset[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \newcommand\blueline[4]{\draw[dblue, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \begin{tikzpicture}
        \bluebox{0}{0}{\textbf{Gather test dataset.}\\(SEC filings, news, social\\media, stock price data)};
        \bluebox{0}{-2}{\textbf{Evaluate correlations}\\\textbf{between media release}\\\textbf{\& price movement.}};
        \bluebox{2}{-4}{\textbf{Change type of}\\\textbf{input media.}};
        \bluebox{0}{-6}{\textbf{Fine-tune training}\\\textbf{on GPT-J.}};
        \bluebox{2}{-8}{\textbf{Change format of}\\\textbf{input prompt.}};
        \bluebox{0}{-10}{\textbf{Evaluate prediction}\\\textbf{accuracy.}};
        \bluebox{0}{-12}{\textbf{Test and evaluate}\\\textbf{on live data.}};
        \bluearrow{0}{0}{0}{-2};
        \bluearrow{-1}{-2}{-1}{-6};
        \blueline{0.25}{-4}{-1}{-4};
        \bluearrow{-1}{-6}{-1}{-10};
        \blueline{0.25}{-8}{-1}{-8};
        \bluearrow{0}{-10}{0}{-12};
        \blueline{1.75}{-10}{4.21}{-10};
        \bluearrownooffset{2.75}{-10}{2.75}{-8.75};
        \blueline{4.25}{-4.04}{4.25}{-10.04};
        \bluearrownooffset{4.29}{-4}{3.75}{-4};
        \blueline{2.75}{-7.25}{2.75}{-5.96};
        \bluearrownooffset{2.75}{-6}{1.75}{-6};
    \end{tikzpicture}
    }
\caption{Execution Flow}
\end{figure}
\section{Implementation}
\section{Conclusion}
The conclusion goes here.

>>>>

\documentclass[conference]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{svg}
\usepackage{float}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}
% \usepackage{flushend}
\begin{document}

@@

By our estimation, the vast majortity of previous works involving sentiment analysis used a pre-processing step to extract sentiment from the news, and then embedded those features into a time-series dataset. News sources were often limited to headlines, tweets and small snippits because of the memory limitations of RNN sentiment classifiers. With the indruduction of large transformer networks \cite{Vaswani2017}, capable of processing large amounts of text like OpenAi's GPT-3 \cite{Brown2020} or Wang \& Komatsuzaki's GPT-J \cite{gpt-j}, we believe a new class of trading network can be created. Our method will encode the current world state in a large text-input wich combines sentiment, real-world facts, and stock price data into a single input. We believe that this new network can be trained to learn to trade like a human.

@@

\begin{figure}[ht]
    \centering
    \scalebox{0.8}{
    \definecolor{lblue}{RGB}{220, 234, 240}
    \definecolor{dblue}{RGB}{0, 21, 79}
    \newcommand\bluebox[3]{\filldraw [draw=dblue,fill=lblue, line width=0.4mm] (#1-1.75,#2-0.75) rectangle (#1+1.75,#2+0.75) node[text=dblue, font=\footnotesize][midway] {\makecell[l]{#3}}}
    \newcommand\bluearrow[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2-0.75) -- (#3,#4+0.75);}
    \newcommand\bluearrownooffset[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \newcommand\blueline[4]{\draw[dblue, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \begin{tikzpicture}
        \bluebox{0}{0}{\textbf{Gather test dataset.}\\(SEC filings, news, social\\media, stock price data)};
        \bluebox{0}{-2}{\textbf{Evaluate correlations}\\\textbf{between media release}\\\textbf{\& price movement.}};
        \bluebox{2}{-4}{\textbf{Change type of}\\\textbf{input media.}};
        \bluebox{0}{-6}{\textbf{Fine-tune training}\\\textbf{on GPT-J.}};
        \bluebox{2}{-8}{\textbf{Change format of}\\\textbf{input prompt.}};
        \bluebox{0}{-10}{\textbf{Evaluate prediction}\\\textbf{accuracy.}};
        \bluebox{0}{-12}{\textbf{Test and evaluate}\\\textbf{on live data.}};
        \bluearrow{0}{0}{0}{-2};
        \bluearrow{-1}{-2}{-1}{-6};
        \blueline{0.25}{-4}{-1}{-4};
        \bluearrow{-1}{-6}{-1}{-10};
        \blueline{0.25}{-8}{-1}{-8};
        \bluearrow{0}{-10}{0}{-12};
        \blueline{1.75}{-10}{4.21}{-10};
        \bluearrownooffset{2.75}{-10}{2.75}{-8.75};
        \blueline{4.25}{-4.04}{4.25}{-10.04};
        \bluearrownooffset{4.29}{-4}{3.75}{-4};
        \blueline{2.75}{-7.25}{2.75}{-5.96};
        \bluearrownooffset{2.75}{-6}{1.75}{-6};
    \end{tikzpicture}
    }
\caption{Execution Flow}
\end{figure}
\section{Implementation}
\section{Conclusion}
The conclusion goes here.
